### 2013-11-20 loadClean.Rmd
Adding the plots

% Loading and cleaning the data

- [back to index](index.html)

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(kaRski)
knitpandoc("loadClean")
```

@@

```{rLoadClean7, eval=TRUE}
#######
# Quality of governance
# library(rustfare)
# datQog <- GetQog(country = c('Armenia','Azerbaijan','Georgia','Russia',
#                    'Ukraine','Moldova','Belarus','Kyrgyzstan',
#                    'Kazakhstan','Tajikistan',
#                    'Uzbekistan','Estonia','Latvia','Lithuania',
#                    'Poland','Czech Republic','Slovakia','Hungary',
#                    'Slovenia','Romania','Bulgaria',
#                    'Italy','Germany','United Kingdom',
#                    'Sweden','France'), 
#        indicator = c("ffp_fsi", # Failed States Index
#                      "wbgi_vae", # World Bank - Voice and Accountability
#                      "undp_hdi", # UNDP Human Development Index
#                      "fh_polity2", # Democracy (Freedom House/Polity)
#                      "uw_gini"))
# # subset the latest value per cntry per indicator
# library(plyr)
# datQogSum <- ddply(datQog, c("cname","indicator"), 
#                    subset, year == max(year))

# datQogSum.w <- dcast(datQogSum, 
#                      cname ~ indicator, 
#                      value.var="value")
# 
# datQogSum.w$cname <-  as.character(datQogSum.w$cname)
# datQogSum.w$cname[datQogSum.w$cname %in% "United Kingdom"] <- "Great Britain"
# 
# datQogSum.w$group_fine[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Georgia')] <- 'Caucasus'
# datQogSum.w$group_fine[datQogSum.w$cname %in% c('Russia','Ukraine','Moldova','Belarus')] <- 'CIS North'
# datQogSum.w$group_fine[datQogSum.w$cname %in% c('Kyrgyzstan','Kazakhstan','Tajikistan','Uzbekistan')] <- 'Central Asia'
# datQogSum.w$group_fine[datQogSum.w$cname %in% c('Estonia','Latvia','Lithuania')] <- 'Baltic States'
# datQogSum.w$group_fine[datQogSum.w$cname %in% c('Poland','Czech Republic','Slovakia','Hungary',
#                                                 'Slovenia','Romania','Bulgaria')] <- 'CEE EU'
# datQogSum.w$group_fine[datQogSum.w$cname %in% c('Italy','Germany','Great Britain','Sweden','France')] <- 'West Europe'
#                          
# datQogSum.w$group_fine <- factor(datQogSum.w$group_fine)
# 
# summary(factor(datQogSum.w$group_fine))
# 
# datQogSum.w$group_general[datQogSum.w$cname %in% c('France','Germany',
#                                                    'Great Britain','Italy','Sweden')] <- 'Western Europe'
# datQogSum.w$group_general[datQogSum.w$cname %in% c('Czech Republic','Estonia',
#                                                    'Hungary','Bulgaria',
#                                                    'Latvia','Lithuania','Poland',
#                                                    'Slovakia','Slovenia','Romania')] <- 'CEE'
# datQogSum.w$group_general[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Belarus',
#                                                    'Georgia','Kazakhstan',
#                                                    'Kyrgyzstan','Moldova',
#                                                    'Tajikistan','Ukraine',
#                                                    'Uzbekistan','Russia')] <- 'CIS'
# 
# datQogSum.w$group_general <- factor(datQogSum.w$group_general, 
#                                     levels=c("Western Europe",
#                                              "CEE",
#                                              "CIS"))
# 
#df.qog <- datQogSum.w
# 
# names(df.qog)[1] <- "cntry"

@@

```{rLoadClean8, eval=TRUE}
# ## GDP change from WB
# ### We need iso2c countrycode
# library(countrycode)
# cntry <- levels(df$cntry) # countrynames
# iso2c <- countrycode(cntry, "country.name", "iso2c")
# iso2c # copy paste into WDI search
# library(WDI)
# # WDIsearch(string='gdp', field='name', cache=NULL)
# wb <- WDI(indicator = c("NY.GDP.MKTP.CD"), 
#           country = c("AL","AM","AZ","BY","BA","BG","HR",
#                       "CZ","EE","FR","GE","DE","GB","HU",
#                       "IT","KZ","KG","LV","LT","MK","MD",
#                       "MN","ME","PL","RO","RU","RS","SK",
#                       "SI","SE","TJ","TR","UA","UZ"), 
#            start = 2007, end = 2010)
# 
# library(reshape2)
# names(wb) <- c("iso2c","cntry","var","year")
# wb.w <- dcast(wb, 
#               cntry ~ year, 
#               value.var="var")
# 
# names(wb.w) <- c("cntry","x2007","x2008","x2009","x2010")
# wb.w$gdpchange07.10 <- wb.w$x2010/wb.w$x2007 * 100 - 100
# gdp <- wb.w[,c(1,6)]
# 
# gdp$cntry[gdp$cntry == 'Russian Federation'] <- 'Russia'
# gdp$cntry[gdp$cntry == 'Kyrgyz Republic'] <- 'Kyrgyzstan'
# gdp$cntry[gdp$cntry == 'United Kingdom'] <- 'Great Britain'
# gdp$cntry[gdp$cntry == 'Slovak Republic'] <- 'Slovakia'

@@

# yhdistetään nää aikaisempien datojen kanssa
# macro <- merge(summary309w,gdp,by="cntry", all.x=TRUE)
# macro <- merge(macro,df.qog,by="cntry")
#save(macro, file="data/macro.RData")
load("data/macro.RData")
macro <- merge(macro,perGini2010,by="cntry")

>>>>

# Loading and cleaning the data

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit2html('loadClean.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))

@@

```{rLoadClean7, eval=TRUE}
#######
# Quality of governance
library(rustfare)
datQog <- GetQog(country = c('Armenia','Azerbaijan','Georgia','Russia',
                   'Ukraine','Moldova','Belarus','Kyrgyzstan',
                   'Kazakhstan','Tajikistan',
                   'Uzbekistan','Estonia','Latvia','Lithuania',
                   'Poland','Czech Republic','Slovakia','Hungary',
                   'Slovenia','Romania','Bulgaria',
                   'Italy','Germany','United Kingdom',
                   'Sweden','France'), 
       indicator = c("ffp_fsi", # Failed States Index
                     "wbgi_vae", # World Bank - Voice and Accountability
                     "undp_hdi", # UNDP Human Development Index
                     "fh_polity2", # Democracy (Freedom House/Polity)
                     "uw_gini"))
# subset the latest value per cntry per indicator
library(plyr)
datQogSum <- ddply(datQog, c("cname","indicator"), 
                   subset, year == max(year))

datQogSum.w <- dcast(datQogSum, 
                     cname ~ indicator, 
                     value.var="value")

datQogSum.w$cname <-  as.character(datQogSum.w$cname)
datQogSum.w$cname[datQogSum.w$cname %in% "United Kingdom"] <- "Great Britain"

datQogSum.w$group_fine[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Georgia')] <- 'Caucasus'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Russia','Ukraine','Moldova','Belarus')] <- 'CIS North'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Kyrgyzstan','Kazakhstan','Tajikistan','Uzbekistan')] <- 'Central Asia'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Estonia','Latvia','Lithuania')] <- 'Baltic States'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Poland','Czech Republic','Slovakia','Hungary',
                                                'Slovenia','Romania','Bulgaria')] <- 'CEE EU'
datQogSum.w$group_fine[datQogSum.w$cname %in% c('Italy','Germany','Great Britain','Sweden','France')] <- 'West Europe'

datQogSum.w$group_fine <- factor(datQogSum.w$group_fine)

summary(factor(datQogSum.w$group_fine))

datQogSum.w$group_general[datQogSum.w$cname %in% c('France','Germany',
                                                   'Great Britain','Italy','Sweden')] <- 'Western Europe'
datQogSum.w$group_general[datQogSum.w$cname %in% c('Czech Republic','Estonia',
                                                   'Hungary','Bulgaria',
                                                   'Latvia','Lithuania','Poland',
                                                   'Slovakia','Slovenia','Romania')] <- 'CEE'
datQogSum.w$group_general[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Belarus',
                                                   'Georgia','Kazakhstan',
                                                   'Kyrgyzstan','Moldova',
                                                   'Tajikistan','Ukraine',
                                                   'Uzbekistan','Russia')] <- 'CIS'

datQogSum.w$group_general <- factor(datQogSum.w$group_general, 
                                    levels=c("Western Europe",
                                             "CEE",
                                             "CIS"))

df.qog <- datQogSum.w

names(df.qog)[1] <- "cntry"

@@

```{rLoadClean8, eval=TRUE}
## GDP change from WB
### We need iso2c countrycode
library(countrycode)
cntry <- levels(df$cntry) # countrynames
iso2c <- countrycode(cntry, "country.name", "iso2c")
iso2c # copy paste into WDI search
library(WDI)
# WDIsearch(string='gdp', field='name', cache=NULL)
wb <- WDI(indicator = c("NY.GDP.MKTP.CD"), 
          country = c("AL","AM","AZ","BY","BA","BG","HR",
                      "CZ","EE","FR","GE","DE","GB","HU",
                      "IT","KZ","KG","LV","LT","MK","MD",
                      "MN","ME","PL","RO","RU","RS","SK",
                      "SI","SE","TJ","TR","UA","UZ"), 
           start = 2007, end = 2010)

library(reshape2)
names(wb) <- c("iso2c","cntry","var","year")
wb.w <- dcast(wb, 
              cntry ~ year, 
              value.var="var")

names(wb.w) <- c("cntry","x2007","x2008","x2009","x2010")
wb.w$gdpchange07.10 <- wb.w$x2010/wb.w$x2007 * 100 - 100
gdp <- wb.w[,c(1,6)]

gdp$cntry[gdp$cntry == 'Russian Federation'] <- 'Russia'
gdp$cntry[gdp$cntry == 'Kyrgyz Republic'] <- 'Kyrgyzstan'
gdp$cntry[gdp$cntry == 'United Kingdom'] <- 'Great Britain'
gdp$cntry[gdp$cntry == 'Slovak Republic'] <- 'Slovakia'

@@

# yhdistetään nää aikaisempien datojen kanssa
macro <- merge(summary309w,gdp,by="cntry", all.x=TRUE)
macro <- merge(macro,df.qog,by="cntry")
macro <- merge(macro,perGini2010,by="cntry")
